---
title: "Win Probability Package"
author: "Jim Albert"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

#### Introduction

Here is a brief illustration of using the WinProbability package just created on my Github site.

Install the package from Github:

```{r}
library(devtools)
install_github("bayesball/WinProbability")
```

Load the package:

```{r}
library(WinProbability)
```

#### Setup

I'm in a folder where I have a raw Retrosheet play-by-play datafile.  Note that the file must be of the form ```allYEAR.csv``` where YEAR is the value input in the function.

```{r}
dir()
```

#### Compute runs expectancies

The ```compute.runs.expectancy``` function:

- Reads in the raw dataset
- Adds a header to the Retrosheet datafile
- Computes the run expectancies and adds these to the datafile

```{r}
d2018 <- compute.runs.expectancy(2018)
```

#### Compute win probabilities

The ```compute.win.probs``` function will

- Compute the win probabilities for all plays.
- The input is the Retrosheet play-by-play data frame with run expectancy values included

```{r}
d2018 <- compute.win.probs(d2018)
```


#### Graph the win probabilities for a game

The ```graph.game``` function will plot the win probabilities for all plays in a specific game.

```{r}
plays <- graph.game(d2018, "SLN201805190")
```


